Make interactive loan word maps

### 2025-06-05 README.qmd
static maps

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Title of your paper goes here"
```

@@

> Authors, (YYYY). _`r Title`_. Name of journal/book <https://doi.org/xxx/xxx>

Our pre-print is online here:

> Authors, (YYYY). _`r Title`_. Name of journal/book, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document
    for manuscript. Includes code to reproduce the figures and tables
    generated by the analysis. It also has a rendered version,
    `paper.docx`, suitable for reading (the code is replaced by figures
    and tables in this file)
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations
  - [:file\_folder:
    supplementary-materials](/analysis/supplementary-materials):
    Supplementary materials including notes and other documents
    prepared and collected during the analysis.

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Loanwords and Trade in West Africa: grains, gold, salt, and iron"
```

@@

> Schreiber, Henning & Gestrich, Nikolas (2025). _`r Title`_. Journal of global archaeology <https://doi.org/xxx/xxx>

@@

  - [:file\_folder: paper](/analysis/paper): Quarto source document. 
    Includes code to reproduce the figures and tables
    generated by the analysis.
  - [:file\_folder: data](/analysis/data): Data used in the analysis.
  - [:file\_folder: figures](/analysis/figures): Plots and other
    illustrations

### 2025-06-05 analysis/paper/loan word maps.qmd
static maps

@@

```{r}
#| label: fonio
#| fig-cap: "fonio word forms"
# create_leaflet_map(data_list$iron, background = "bw") #uncomment to run
```

@@

```{r}
#| label: save-maps
#| eval: false
# save_maps(data_list)  #uncomment to run
```

@@

```{r}
library(rnaturalearth)

>>>>

We need to standardise the "form" column to be lowercase

```{r}
data_list <- purrr::map(data_list, ~ {
  .x |> 
    dplyr::mutate(dplyr::across(.cols = starts_with("form"), ~ tolower(.)))
})
```

@@

```{r}
#| label: fonio
#| fig-cap: "fonio word forms"

 # create_leaflet_map(data_list$iron, background = "colour") #uncomment line to run
```

@@

```{r}
#| label: save-maps
#| eval: false

 save_maps(data_list, background = "colour")  #uncomment to run

@@

```{r}
library(rnaturalearth)
library(rnaturalearthdata)
